---
title: "Teaching Lab Report"
output: 
  html_document:
    code_folding: hide
    theme:
      bg: "white"
      fg: "black"
      primary: "#04abeb"
      secondary: "#00DAC6"
      base_font:
        Calibri
      heading_font:
        Montserrat
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
library(tidyverse)
library(TeachingLab)
knitr::opts_chunk$set(echo = F, warning = F, message = F)
# library(surveymonkey)
# options(sm_oauth_token = "BjVjlV9MiVBgfe1XpS2xPS547c6gkAygKWAgm4Vv539-KbFct5lsqyVGRCZun0GDt21lnJrgn9hDvSjF.KybF58vc.P.jdeKJ8A2UEUHnE2.50e0lp.86EmQmy8-y9tm")
# session_survey <- surveymonkey::fetch_survey_obj(id = 308115193) %>%
#   surveymonkey::parse_survey() %>%
#   dplyr::mutate(date_created = lubridate::date(date_created)) %>%
#   dplyr::mutate(`Select your course.` = dplyr::coalesce(`Select your course.`, `Select your course._2`, `Select your course._3`,
#                                           `Select your course._4`, `Select your course._5`, `Select your course._6`)) %>%
#   dplyr::mutate(Date = lubridate::mdy(`Select the date for this session. - \n    Date / Time\n`)) %>%
#   # Fix this cluttering of names the others result in a bunch of differernt formats
#   dplyr::mutate(dplyr::across(c("Select the name of your facilitator.", "Select the name of your facilitator. - Other (please specify)",
#                   "Select the name of your facilitator._2", "Select the name of your facilitator. - Other (please specify)_2",
#                   "Select the name of your facilitator._3", "Select the name of your facilitator. - Other (please specify)_3"), ~ dplyr::na_if(.x, "Name"))) %>%
#   dplyr::mutate(Facilitator = dplyr::coalesce(`Select the name of your facilitator.`,
#                                 `Select the name of your facilitator._2`,
#                                 `Select the name of your facilitator._3`,
#                                 `Select the name of your facilitator. - Other (please specify)_2`,
#                                 `Select the name of your facilitator. - Other (please specify)_3`),
#          Facilitation_Feedback = dplyr::coalesce(`What additional feedback do you have about their facilitation skills?`,
#                                           `What additional feedback do you have about their facilitation skills?_2`,
#                                           `What additional feedback do you have about their facilitation skills?_3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.`,
#                   `How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.`,
#                   `How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.`,
#                   `How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.`,
#                   `How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session._3`)) %>%
# dplyr::mutate(`How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs.` =
#          dplyr::coalesce(`How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs.`,
#                   `How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs._2`,
#                   `How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs._3`))
# 
# filtered <- session_survey %>%
#   dplyr::filter(`Select your site (district, parish, network, or school).` == "San Diego Unified School District, CA")

# write_rds(filtered, here::here("Data-Clean/surveymonkey_session_sandiego.rds"))

df <- read_rds(here::here("Data-clean/surveymonkey_session_sandiego.rds")) %>%
  select(-survey_id, -collector_id, -respondent_id, -date_created, -date_modified, -response_status)

df_split <- df %>%
  group_by(Facilitator) %>%
  group_split()

map(1:length(df_split), ~ assign(df_split[[.x]]$Facilitator[1] %>% str_replace_all(., " ", "_"), 
                                 df_split[[.x]],
                                 envir = .GlobalEnv))
```

## San Diego Participant Feedback

Below I compile participant feedback for all quantifiable questions for each facilitator on the left side of the tab, and qualitative feedback on the right side.

## Facilitator Feedback {.tabset .tabset-pills}

### Callie Herring

```{r}
callie_agree <- Callie_Herring %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
callie_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", callie_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Elizabeth Van Hoesen

```{r}
elizabeth_agree <- Elizabeth_Van_Hoesen %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
elizabeth_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", elizabeth_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Emily Howard

```{r}
emily_agree <- Emily_Howard %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
emily_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", emily_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Evan Rushton

```{r}
evan_agree <- Evan_Rushton %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
evan_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", evan_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Hanady Elsayed

```{r}
hanady_agree <- Hanady_Elsayed %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
hanady_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", hanady_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Kristen Taylor

```{r}
kristen_agree <- Kristen_Taylor %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
kristen_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", kristen_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Mary Shaw-Lewis

```{r}
mary_agree <- `Mary_Shaw-Lewis` %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
mary_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", mary_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Megan Lewis

```{r}
megan_agree <- Megan_Lewis %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
megan_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", megan_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Patricia Thibodeaux

```{r}
patricia_agree <- Patricia_Thibodeaux %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
patricia_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", patricia_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Ryan Colon

```{r}
ryan_agree <- Ryan_Colon %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
ryan_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", ryan_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```

### Spring Mercadel

```{r}
spring_agree <- Spring_Mercadel %>%
  select(c(
          "How much do you agree with the following statements about this facilitator today? - They demonstrated  deep knowledge of the content they facilitated.",
          "How much do you agree with the following statements about this facilitator today? - They facilitated the content clearly.",
          "How much do you agree with the following statements about this facilitator today? - They effectively built a safe learning community.",
          "How much do you agree with the following statements about this facilitator today? - They were fully prepared for the session.",
          "How much do you agree with the following statements about this facilitator today? - They responded to the group’s needs."
        )) %>%
        pivot_longer(everything(), names_to = "Question", values_to = "Response") %>%
        drop_na() %>%
        dplyr::mutate(Question = str_remove_all(
          Question,
          "How much do you agree with the following statements about this facilitator today\\? - "
        )) %>%
        group_by(Question, Response) %>%
        count() %>%
        ungroup() %>%
        group_by(Question) %>%
        mutate(Question = str_wrap(Question, width = 30)) %>%
        summarise(
          n = n,
          Response = Response,
          Percent = n / sum(n) * 100
        )
spring_agree %>%
  ggplot(aes(x = Question, y = Percent, fill = factor(Response))) +
        geom_col() +
        geom_text(aes(label = if_else(Percent >= 3, paste0(round(Percent), "%"), "")), position = position_stack(vjust = 0.5)) +
        scale_fill_manual(values = c(
          "(1) Strongly disagree" = "#040404", "(2) Disagree" = "#032E3F",
          "(3) Neither agree nor disagree" = "#02587A", "(4) Agree" = "#0182B4", "(5) Strongly agree" = "#00ACF0"
        )) +
        labs(
          fill = "", title = "Percent that Agree/Strongly Agree with\nEach of the Following Statements",
          x = "", y = "", caption = paste0("n = ", spring_agree %>% group_by(Question) %>% 
            summarise(n = sum(n)) %>% select(n) %>% slice(1))
        ) +
        coord_flip() +
        guides(fill = guide_legend(reverse = T)) +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_tl(legend = T) +
        theme(
          axis.text.x = element_blank(),
          axis.text.y = element_text(lineheight = 1.1, size = 14),
          legend.position = "bottom",
          plot.title = element_text(lineheight = 1.1, size = 20, face = "bold"),
          legend.key.size = unit(1.25, "cm"),
          legend.text = element_text(size = 9)
        )
```


