---
title: "list_sites_know_assess"
author: "Duncan Gates"
date: "1/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googlesheets4)

surveys <- surveymonkey::browse_surveys() %>%
  dplyr::mutate(responses = map(id, ~ surveymonkey::fetch_survey_obj(id = .x)$`response_count`))

surveys_final <- surveys %>%
  dplyr::mutate(responses = as.numeric(responses)) %>%
  dplyr::filter(responses > 0 & str_detect(title, "ELA|Math"))

all_sites <- read_sheet("https://docs.google.com/spreadsheets/d/11jlo9UeWxZGwunhDb24hZBwAKc5b8ZKM9AYNWZaUyZY/edit#gid=0",
                        sheet = 1,
                        range = "C3:C",
                        col_names = "Site")

sites <- all_sites$Site %>%
  purrr::keep( ~ !str_detect(.x, "Rochester")) %>%
  append("Rochester City School District, NY") %>%
  sort()

sites %>% 
  clipr::write_clip()

# surveys$title %>% paste("## ", .) %>%
#   clipr::write_clip()
```

##  ELA: CRSE PLC

```{r}
ela_crse_plc_sites <- surveymonkey::fetch_survey_obj(312484554) %>%
  surveymonkey::parse_survey() %>%
  pull(`Please select your site (district, parish, network, or school)`) %>%
  levels()

setdiff(sites, ela_crse_plc_sites)

different <- c("Fannie Lou Hamer, NY",
               "Amistad Dual Language, NY",)

c("CityYear, NY",
  "Hostos Lincoln Academy of Science, NY",
  "NYC District 6 - MS311, NY",
  "NYC District 9 - District-wide, NY",
  "NYC District 10 - PS 386, NY",
  "NYC District 11 - District-wide, NY",
  "NYC District 11 - IS 498, NY",
  "NYC District 11 - MS 127, NY",
  "NYC District 11 - PS 178, NY",
  "NYC District 11 - PS 19, NY",
  "NYC District 11 - PS 481, NY",
  "NYC District 11 - PS 83, NY",
  "NYC District 12 - EMST-IS 190, NY",
  "NYC District 12 - MS 286, NY",
  "NYC District 27, Channel View School for Research, NY",
  "Robinhood Schools (NYC), NY",
  "St. Charles Parish, LA") %>% clipr::write_clip()

```

##  ELA General: Cycle of Inquiry - Speaking & Listening

```{r}
ela_general_cycle_inquiry_speaking_listening_sites <- surveymonkey::fetch_survey_obj(315708558) %>%
  surveymonkey::parse_survey() %>%
  pull(`Please select your site (district, parish, network, or school)`) %>%
  levels()

setdiff(sites, ela_general_cycle_inquiry_speaking_listening_sites)
```

##  Math: Cycle of Inquiry I - Eliciting Student Thinking

```{r}

```

##  Math: Bootcamp

```{r}

```

##  ELA: Guidebooks Diverse Learners Cycle of Inquiry - Vocabulary

```{r}

```

##  ELA: Cycle of Inquiry - Curriculum Flex Foundational Skills

```{r}

```

##  ELA: Bootcamp - General

```{r}

```

##  Math: Bootcamp - EIC

```{r}

```

##  Math: Accelerating Learning

```{r}

```

##  ELA: Bootcamp - Foundational Skills Bootcamp Skills (K-2)

```{r}

```

##  Math: Accelerating Learning - EIC

```{r}

```

##  ELA: Guidebooks Diverse Learners Bootcamp Writing

```{r}

```

##  ELA: Guidebooks Diverse Learners Bootcamp - Leader

```{r}

```

##  ELA: HQIM & Enrichment

```{r}

```

##  ELA: Guidebooks Diverse Learners Bootcamp - Teacher

```{r}

```

##  School Leaders: ELA

```{r}

```

##  Math: Cycle of Inquiry V- Sequencing and Connecting Representations

```{r}

```
