---
title: "Example Report Comparing All Facilitators"
author: "Teaching Lab Monthly Facilitator Review"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmdformats::readthedown:
    css: styles.css
    self_contained: true # Other options are downcute, material, readthedown, html_clean, html_docco, lockdown, https://github.com/juba/rmdformats
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: kate # Also can do tango
    number_sections: false
    includes:
      after_body: footer.html
---

```{r setup, echo = F, cache = F, include = F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(tidyverse)
library(lubridate)
library(ggiraph)
library(gt)
library(reactable)
library(reactablefmtr)
library(scales)
library(htmltools)
library(htmlwidgets)
library(glue)
library(here)
sheets_data <- read_rds(here("Data/google_sheets_data.rds"))

col <- colorRampPalette(c("#040404", "#04ABEB"))

options(width = 2000) # Adjust the width 
```

```{r echo = F}
htmltools::tagList(rmarkdown::html_dependency_font_awesome()) # Needed so fa's in footer will show
```

# List of Report Types

- Snapshot of all PL work (for our team, funders, board, website, impact report)

- Facilitator report (only has data for that facilitator) - does not include NPS

- Report comparing all facilitators (for facilitator development)

# Example of a Plot

Note that I could add interactivity here for each point so that when you hover you can see what the response to any given question associated with the point is.

```{r}
# All time plot
sheets_data %>%
  drop_na(`Select the name of your first facilitator.`) %>%
  mutate(`Select the name of your first facilitator.` = str_replace(`Select the name of your first facilitator.`,
                                                                    "Ryan Mateo Sharnbroich",
                                                                    "Ryan Sharnbroich")) %>%
  ggplot(aes(x = `Select the name of your first facilitator.`, 
                               y = `How likely are you to recommend this professional learning to a colleague or friend?`)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(alpha = 0.3, width = 0.15, aes(color = `Select the name of your first facilitator.`)) +
  coord_flip() +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
  scale_color_manual(values = col(length(unique(sheets_data$`Select the name of your first facilitator.`)))) +
  labs(x = "", title = "Each Facilitator's Scores All Time") +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        text = element_text(family = "Open Sans"),
        plot.title = element_text(hjust = 0.5))

sheets_data %>%
  drop_na(`Select the name of your first facilitator.`) %>%
  mutate(`Select the name of your first facilitator.` = str_replace(`Select the name of your first facilitator.`,
                                                                    "Ryan Mateo Sharnbroich",
                                                                    "Ryan Sharnbroich"),
         Month = lubridate::month(Date, label = T)) %>%
  filter(Month == "Feb") %>% # Filter for current month
  ggplot(aes(x = `Select the name of your first facilitator.`, 
                               y = `How likely are you to recommend this professional learning to a colleague or friend?`)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(alpha = 0.7, width = 0.15, aes(color = `Select the name of your first facilitator.`)) +
  coord_flip() +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
  scale_color_manual(values = col(length(unique(sheets_data$`Select the name of your first facilitator.`)))) +
  labs(x = "", title = glue::glue("Each Facilitator's Scores in the Month of February")) +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        text = element_text(family = "Open Sans", color = "black"),
        axis.text = element_text(color = "black"),
        plot.title = element_text(hjust = 0.5))

# Just this month plot
sheets_data %>%
  drop_na(`Select the name of your first facilitator.`) %>%
  mutate(`Select the name of your first facilitator.` = str_replace(`Select the name of your first facilitator.`,
                                                                    "Ryan Mateo Sharnbroich",
                                                                    "Ryan Sharnbroich"),
         Month = lubridate::month(Date, label = T),
         Month2 = lubridate::month(Date)) %>%
  filter(Month2 == month(Sys.Date())) %>% # Filter for current month
  ggplot(aes(x = `Select the name of your first facilitator.`, 
                               y = `How likely are you to recommend this professional learning to a colleague or friend?`)) +
  geom_boxplot(alpha = 0) +
  geom_jitter(alpha = 0.7, width = 0.15, aes(color = `Select the name of your first facilitator.`)) +
  coord_flip() +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
  scale_color_manual(values = col(length(unique(sheets_data$`Select the name of your first facilitator.`)))) +
  labs(x = "", title = glue::glue("Each Facilitator's Scores in the Month of {month(Sys.Date(), label = T, abbr = F)}")) +
  theme_minimal() + 
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        text = element_text(family = "Open Sans", color = "black"),
        axis.text = element_text(color = "black"),
        plot.title = element_text(hjust = 0.5))
ggsave(here(paste0("Images/", "facilitator_", month(Sys.Date(), abbr = F, label = T), "_plot.png")), width = 16, height = 9)
```

As of yet there are no scores in march - this graph will autofill once data is updated!

# Table Example

```{r}
# Survey response filter for relevent columns
survey_responses <- sheets_data %>%
  select(`How likely are you to recommend this professional learning to a colleague or friend?`, 
         `I am satisfied with the overall quality of this course.`, 
         `I felt a sense of community with the other participants in this course even though we were virtual.`,
         `Select your course.`,
         `Date`,
         `Select the name of your first facilitator.`,
         `S/he facilitated the content clearly #1`,
         `S/he effectively built a community of learners #1`) %>%
  drop_na(`How likely are you to recommend this professional learning to a colleague or friend?`, `Select the name of your first facilitator.`) %>%
  mutate(Date = format(`Date`, '%b, %d %Y')) %>%
  dplyr::arrange(desc(`How likely are you to recommend this professional learning to a colleague or friend?`))
# Calculate percent agree/strongly agree
survey_percents <- survey_responses %>%
  select(-`How likely are you to recommend this professional learning to a colleague or friend?`) %>%
  group_by(`Select the name of your first facilitator.`) %>%
  summarise(across(where(is.numeric), ~ round(length(which(.x %in% c(4, 5)))/length(.x), 4)))
# NPS calculations
survey_nps <- survey_responses %>%
  select(`How likely are you to recommend this professional learning to a colleague or friend?`,
         `Select the name of your first facilitator.`) %>%
  group_by(`Select the name of your first facilitator.`) %>%
  summarise(NPS = round(((length(which(`How likely are you to recommend this professional learning to a colleague or friend?` %in% c(9, 10)))/
                           length(`How likely are you to recommend this professional learning to a colleague or friend?`)) -
                          (length(which(`How likely are you to recommend this professional learning to a colleague or friend?` %in% c(0:6)))/
                           length(`How likely are you to recommend this professional learning to a colleague or friend?`)))*100, 2))
# Join nps and percent agree/strongly agree
survey_facilitators_final <- left_join(survey_percents, survey_nps, by = "Select the name of your first facilitator.")
```

<div style = "width:180%; height:auto; margin: auto;">
```{r gt-table-1}
survey_facilitators_final %>%
  arrange(desc(NPS)) %>%
  gt() %>%
  tab_header(
    title = md("&#128200; **Facilitator Scoring** &#128201;"),
    subtitle = md("Sorted *Best-Worst NPS*, **%'s Represent Proportion that Strongly Agree/Agree**")
  ) %>%
  fmt_percent(
    columns = vars(`I am satisfied with the overall quality of this course.`,
                   `I felt a sense of community with the other participants in this course even though we were virtual.`,
                   `S/he facilitated the content clearly #1`,
                   `S/he effectively built a community of learners #1`),
    decimals = 1
  ) %>%
  cols_label(
    `Select the name of your first facilitator.` = md("**Facilitator**"),
    `I am satisfied with the overall quality of this course.` = md("**I am satisfied with the overall quality of this course**"),
    `I felt a sense of community with the other participants in this course even though we were virtual.` = md("**I felt a sense of community with the other participants in this course even though we were virtual**"),
    `S/he facilitated the content clearly #1` = md("**S/he facilitated the content clearly**"),
    `S/he effectively built a community of learners #1` = md("**S/he effectively built a community of learners #1**"),
    NPS = md("**NPS**")
  ) %>%
  cols_width(
    vars(NPS) ~ px(110),
         everything() ~ px(250)
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  data_color(columns = vars(NPS),
             colors = scales::col_numeric(
               palette = col(nrow(survey_responses))
               %>% as.character(),
             domain = NULL)
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "right",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = vars(NPS,
                       `Select the name of your first facilitator.`)
      )
    )
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = vars(NPS,
                       `Select the name of your first facilitator.`)
      )
    )
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "bottom",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_column_labels(
        columns = gt::everything()
      )
    )
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "right",
        color = "gray50",
        weight = px(1.5)
      )
    ),
    locations = list(
      cells_body(
        columns = vars(`I am satisfied with the overall quality of this course.`, 
                       `I felt a sense of community with the other participants in this course even though we were virtual.`,
                       `S/he facilitated the content clearly #1`,
                       `Select the name of your first facilitator.`)
      )
    )
  ) %>%
  tab_options(
    summary_row.background.color = "#ACEACE80",
    grand_summary_row.background.color = "#990000",
    row_group.background.color = "#FFEFDB80",
    heading.background.color = "#04ABEB", # Main Heading Background
    column_labels.background.color = "#EFFBFC",
    stub.background.color = "#EFFBFC",
    table.font.color = "#323232",
    table.font.names = "Open Sans",
    table_body.hlines.color = "#989898",
    table_body.border.top.color = "#989898",
    heading.border.bottom.color = "#989898",
    row_group.border.top.color = "#989898",
    row_group.border.bottom.style = "none",
    stub.border.style = "dashed",
    stub.border.color = "#989898",
    stub.border.width = "1px",
    summary_row.border.color = "#989898")
```
</div>
# A Monthly Filtered Table

```{r gt-table-data-2}
# Survey response filter for relevent columns
survey_responses_february <- sheets_data %>%
  select(`How likely are you to recommend this professional learning to a colleague or friend?`, 
         `I am satisfied with the overall quality of this course.`, 
         `I felt a sense of community with the other participants in this course even though we were virtual.`,
         `Select your course.`,
         `Date`,
         `Select the name of your first facilitator.`,
         `S/he facilitated the content clearly #1`,
         `S/he effectively built a community of learners #1`) %>%
  drop_na(`How likely are you to recommend this professional learning to a colleague or friend?`, `Select the name of your first facilitator.`) %>%
  mutate(Date = month(Date, label = T, abbr = F)) %>%
  filter(Date == "February") %>%
  dplyr::arrange(desc(`How likely are you to recommend this professional learning to a colleague or friend?`))
# Calculate percent agree/strongly agree
survey_percents_february <- survey_responses_february %>%
  select(-`How likely are you to recommend this professional learning to a colleague or friend?`) %>%
  group_by(`Select the name of your first facilitator.`) %>%
  summarise(across(where(is.numeric), ~ round(length(which(.x %in% c(4, 5)))/length(.x), 4)))
# NPS calculations
survey_nps_february <- survey_responses_february %>%
  select(`How likely are you to recommend this professional learning to a colleague or friend?`,
         `Select the name of your first facilitator.`) %>%
  group_by(`Select the name of your first facilitator.`) %>%
  summarise(NPS = round(((length(which(`How likely are you to recommend this professional learning to a colleague or friend?` %in% c(9, 10)))/
                           length(`How likely are you to recommend this professional learning to a colleague or friend?`)) -
                          (length(which(`How likely are you to recommend this professional learning to a colleague or friend?` %in% c(0:6)))/
                           length(`How likely are you to recommend this professional learning to a colleague or friend?`)))*100, 2))
# Join nps and percent agree/strongly agree
survey_facilitators_february <- left_join(survey_percents_february, survey_nps_february, by = "Select the name of your first facilitator.")
```

<div style = "width:180%; height:auto; margin: auto;">
```{r}
survey_facilitators_february %>%
  arrange(desc(NPS)) %>%
  gt() %>%
  tab_header(
    title = md("&#128200; **Facilitator Scoring in February** &#128201;"),
    subtitle = md("Sorted *Best-Worst NPS*, **%'s Represent Proportion that Strongly Agree/Agree**")
  ) %>%
  fmt_percent(
    columns = vars(`I am satisfied with the overall quality of this course.`,
                   `I felt a sense of community with the other participants in this course even though we were virtual.`,
                   `S/he facilitated the content clearly #1`,
                   `S/he effectively built a community of learners #1`),
    decimals = 1
  ) %>%
  cols_label(
    `Select the name of your first facilitator.` = md("**Facilitator**"),
    `I am satisfied with the overall quality of this course.` = md("**I am satisfied with the overall quality of this course**"),
    `I felt a sense of community with the other participants in this course even though we were virtual.` = md("**I felt a sense of community with the other participants in this course even though we were virtual**"),
    `S/he facilitated the content clearly #1` = md("**S/he facilitated the content clearly**"),
    `S/he effectively built a community of learners #1` = md("**S/he effectively built a community of learners #1**"),
    NPS = md("**NPS**")
  ) %>%
  cols_width(
    vars(NPS) ~ px(110),
         everything() ~ px(250)
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  data_color(columns = vars(NPS),
             colors = scales::col_numeric(
               palette = col(nrow(survey_responses))
               %>% as.character(),
             domain = NULL)
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "right",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = vars(NPS,
                       `Select the name of your first facilitator.`)
      )
    )
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "left",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_body(
        columns = vars(NPS,
                       `Select the name of your first facilitator.`)
      )
    )
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "bottom",
        color = "black",
        weight = px(3)
      )
    ),
    locations = list(
      cells_column_labels(
        columns = gt::everything()
      )
    )
  ) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = "right",
        color = "gray50",
        weight = px(1.5)
      )
    ),
    locations = list(
      cells_body(
        columns = vars(`I am satisfied with the overall quality of this course.`, 
                       `I felt a sense of community with the other participants in this course even though we were virtual.`,
                       `S/he facilitated the content clearly #1`,
                       `Select the name of your first facilitator.`)
      )
    )
  ) %>%
  tab_options(
    summary_row.background.color = "#ACEACE80",
    grand_summary_row.background.color = "#990000",
    row_group.background.color = "#FFEFDB80",
    heading.background.color = "#04ABEB", # Main Heading Background
    column_labels.background.color = "#EFFBFC",
    stub.background.color = "#EFFBFC",
    table.font.color = "#323232",
    table.font.names = "Open Sans",
    table_body.hlines.color = "#989898",
    table_body.border.top.color = "#989898",
    heading.border.bottom.color = "#989898",
    row_group.border.top.color = "#989898",
    row_group.border.bottom.style = "none",
    stub.border.style = "dashed",
    stub.border.color = "#989898",
    stub.border.width = "1px",
    summary_row.border.color = "#989898")
```
</div>

# Example with Summary Statistics

<div style = "width:180%; height:auto; margin: auto;">
```{r}
numeric_averages <- sheets_data %>%
  mutate(Month = lubridate::month(Date, label = T, abbr = F)) %>%
  group_by(Month) %>%
  select(-`How likely are you to recommend this professional learning to a colleague or friend?`) %>%
  summarise(across(where(is.numeric), ~ round(length(which(.x %in% c(4, 5)))/length(.x), 4))) %>%
  select(-`S/he effectively built a community of learners #3`, -`S/he facilitated the content clearly #3`) %>%
  arrange(Month) %>%
  mutate(`S/he facilitated the content clearly` = round((`S/he facilitated the content clearly #1` + `S/he facilitated the content clearly #2`)/2, 2),
         `S/he effectively built a community of learners` = round((`S/he effectively built a community of learners #1` + `S/he effectively built a community of learners #2`)/2, 2)) %>%
  select(-`S/he effectively built a community of learners #1`, -`S/he effectively built a community of learners #2`,
         -`S/he facilitated the content clearly #1`, -`S/he facilitated the content clearly #2`)

nps_average <- sheets_data %>%
  mutate(Month = lubridate::month(Date, label = T, abbr = F)) %>%
  select(Month, `How likely are you to recommend this professional learning to a colleague or friend?`) %>%
  group_by(Month) %>%
  summarise(NPS = round(((length(which(`How likely are you to recommend this professional learning to a colleague or friend?` %in% c(9, 10)))/
                           length(`How likely are you to recommend this professional learning to a colleague or friend?`)) -
                          (length(which(`How likely are you to recommend this professional learning to a colleague or friend?` %in% c(0:6)))/
                           length(`How likely are you to recommend this professional learning to a colleague or friend?`)))*100, 2))
# numeric_average <- round(colMeans(numeric_averages[-1], na.rm = T), 2)
# numeric_average <- purrr::prepend(numeric_average, list("Month" = "Average"))
# numeric_averages <- bind_rows(numeric_averages, numeric_average)
numeric_averages <- left_join(numeric_averages, nps_average, by = c("Month")) %>%
  mutate(Month = factor(Month, levels = c("July", "August", "September", "October", "November", "December", "January", "February", "March", "April", "May", "June"))) %>%
  arrange(Month)
```

```{css, echo = FALSE}
.border-left {
  border-left: 2px solid #555;
}

.border-right {
  border-right: 2px solid #555;
}

.monthly-tbl {
  font-family: "Open Sans";
}

.example-title {
  margin-top: 3px;
  padding: -10px;
  font-size: 20px;
}
```

```{r reactable}
numeric_reactable <- reactable::reactable(numeric_averages,
                                          # Add theme for the top border
                                          theme = reactableTheme(
                                            # style = list(fontFamily = "Open Sans Light Italic"),
                                            headerStyle = list(
                                              "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
                                              "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
                                              borderColor = "#555"
                                            ),
                                            footerStyle = list(
                                              "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
                                              "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
                                              borderColor = "#555"
                                            )
                                          ),
                                          columns = list(
                                            Month = colDef(footer = "Average",
                                                           # Add border to right of column
                                                           class = "border-right",
                                                           width = 100,
                                                           style = list(fontWeight = "bold")),
                                            `I am satisfied with the overall quality of this course.` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`I am satisfied with the overall quality of this course.`)*100, 2), "%")),
                                            `The topics for this course were relevant for my role.` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`The topics for this course were relevant for my role.`)*100, 2), "%")),
                                            `The independent online work activities were well-designed to help me meet the learning targets.` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`The independent online work activities were well-designed to help me meet the learning targets.`)*100, 2), "%")),
                                            `The Zoom course activities were well-designed to help me meet the learning targets.` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`The Zoom course activities were well-designed to help me meet the learning targets.`)*100, 2), "%")),
                                            `I felt a sense of community with the other participants in this course even though we were virtual.` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`I felt a sense of community with the other participants in this course even though we were virtual.`)*100, 2), "%")),
                                            `This course helped me navigate remote and/or hybrid learning during COVID-19.` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`This course helped me navigate remote and/or hybrid learning during COVID-19.`)*100, 2), "%")),
                                            `How likely are you to apply this learning to your practice in the next 4-6 weeks?` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`How likely are you to apply this learning to your practice in the next 4-6 weeks?`)*100, 2), "%")),
                                            `How likely are you to recommend this professional learning to a colleague or friend?` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`How likely are you to recommend this professional learning to a colleague or friend?`)*100, 2), "%")),
                                            `S/he facilitated the content clearly` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`S/he facilitated the content clearly`)*100, 2), "%")),
                                            `S/he effectively built a community of learners` = 
                                              colDef(footer = paste0(round(mean(numeric_averages$`S/he effectively built a community of learners`)*100, 2), "%")),
                                            NPS =
                                              colDef(cell = data_bars_gradient(numeric_averages, 
                                                                               colors = rev(col(10))),
                                                     footer = round(mean(numeric_averages$NPS), 2),
                                                     style = list(backgroundColor = "white",
                                                                  fontWeight = "bold"),
                                                     width = 120,
                                                     class = "border-left")
                                          ),
  defaultColDef = colDef(cell = color_tiles(data = numeric_averages, colors = col(5)[3:5], number_fmt = scales::percent),
                         format = colFormat(percent = T, digits = 2),
                         footerStyle = list(fontWeight = "bold"),
                         headerClass = "average-score-header", align = "center"),
  highlight = T,
  compact = T,
  borderless = F,
  class = "monthly-tbl"
)

div(class = "example",
  div(class = "example-header",
      div(class = "example-title", HTML("<center><h1 style='color:#045777;background-color: hsl(205, 100%, 36%);color: hsl(0, 0%, 20%);font-family: 'Josef Xuereb's Friends';padding-top:0px;margin: 0px;'>Percent that Agree/Strongly Agree w/ Statements Per Month</h1></center>")),
      numeric_reactable
  )
)
```
</div>
```{r eval = F}
saveWidget(widget = numeric_reactable, file = here("HTML/monthly_table.html"), selfcontained = T)
save_html(html = numeric_reactable, file = here("HTML/monthly_table.html"))
webshot2::webshot(url = here("HTML/monthly_table.html"),
                  file = here("Images/monthly_table.png"), vwidth = 900, vheight = 1200, delay = 3)
```

##### TESTING
For all time
```{r}
test <- teaching_df %>%
      select(`Date for the session`, `% Satisfied With The Overall Quality Of Today's Professional Learning Session`, 
             `% Who Say Today's Topic Was Relevant For My Role`, 
             `% Who Say Activities Of Today's Session Were Well-Designed To Help Me Learn`, 
             `How Likely Are You To Apply This Learning To Your Practice In The Next 4-6 Weeks?`, 
             `S/He Facilitated The Content Clearly`, 
             `S/He Effectively Built A Community Of Learners`) %>%
      pivot_longer(!`Date for the session`, names_to = "question", values_to = "answer") %>%
      dplyr::filter(answer != "No Response") %>% # Filter out non-responses
      dplyr::group_by(answer, question) %>% # Group by input variable
      dplyr::summarise(n = n()) %>% # Get count of variable
      dplyr::group_by(answer) %>%
      dplyr::mutate(percent = round(100 * (n / sum(n)), 2)) %>% # Make a percent column without non-responses
      dplyr::mutate(answer = factor(answer, levels = c("Strongly agree", "Agree", "Neither agree nor disagree", "Disagree", "Strongly disagree"))) %>%
      dplyr::relocate(percent, .before = n) %>%
          group_by(question) %>%
          # mutate(percent = factor(percent, levels = unique(percent))) %>%
          arrange(desc(max(percent)))

```

Time series
```{r}
test <- teaching_df %>%
      select(`Date for the session`, newcols[c(5:8, 10:11, 14:15)]) %>%
      pivot_longer(!`Date for the session`, names_to = "question", values_to = "answer") %>%
      dplyr::filter(`answer` != "No Response") %>% # Filter out non-responses
      dplyr::group_by(question, `Date for the session`) %>% # Group by input variable
      mutate(`Number Agree/Disagree` = n()) %>%
      mutate(Rating = case_when(answer %in% c("Agree", "Strongly agree") ~ "Agree/Strongly Agree",
                                  answer %in% c("Neither agree nor disagree", "Disagree", "Strongly disagree") ~ "Neither/Disagree/Strongly Disagree"),
               `Date for the session` = paste0(month(`Date for the session`, label = T, abbr = F), ", ", year(`Date for the session`))) %>%
  ungroup() %>%
        group_by(`Date for the session`, question) %>%
        mutate(Percent = `Number Agree/Disagree`/sum(`Number Agree/Disagree`)*100) %>%
        filter(Rating == "Agree/Strongly Agree") %>%
        group_by(`Date for the session`, Rating, question) %>%
        summarise(Percent = round(sum(Percent), 2))
```

Joining first and second facilitators

```{r}
one_content_clear <- teaching_df %>%
  select(`S/He Effectively Built A Community Of Learners (First Facilitator)`, `S/He Facilitated The Content Clearly (Second Facilitator)`) %>%
  pivot_longer(cols = everything()) %>%
  select(value) %>%
  rename(`S/He Effectively Built A Community Of Learners` = value)

one_community_learners <- teaching_df %>%
  select(`S/He Facilitated The Content Clearly (First Facilitator)`, `S/He Effectively Built A Community Of Learners (Second Facilitator)`) %>%
  pivot_longer(cols = everything()) %>%
  select(value) %>%
  rename(`S/He Effectively Built A Community Of Learners` = value)
```







# Just some fake data for AWS Pricing

```{r}
fake_data <- tibble(hours = 1:100, price = 3.97*hours)

ggplot(fake_data, aes(x = hours, y = price)) + 
  geom_line() +
  geom_vline(linetype = "dashed", color = "magenta4", xintercept = 60) +
  geom_text(color = "magenta4", aes(x = 50, y = 300, label = "My Estimate:")) +
  labs(x = "Server Hours", y = "Price") +
  scale_y_continuous(labels = scales::dollar) +
  theme_bw()
```





